Evolution of ORM Systems: Formal Foundations

### 2013-01-17 doc/description.tex
addTable works with non-empty FK set

\paragraph{Add Table} The transformation creates a new table in the database. The new table should not contain any foreign keys.
\begin{align*}
	\mathbf{addTable} : Table* \times Database \rightarrow Database \\ 
	addTable(t, d) = \begin{cases}
		\inference{|t| > 1}{addTable(head(t),d) \bullet addTable(tail(t), d)}
\\ \\	
		\inference{|t| = 1 \wedge \forall e \in tables(d) \wedge name(t) \neq name(e) \\ \wedge foreignKeys(t) = \varnothing }{tables(d) \cup t}
\\ \\
		Inconsistent \;d 
	 \end{cases}\\ 
	t = Table*, d \lhd Database
\end{align*}

@@

The $CopyProperty$ function can be implemented as a transformation composed by operations for adding and removing property, nevertheless this composition would not work with instances, therefore transformation to update data are used.
\begin{align*}
	\mathbf{CopyProperty} : Label \times Label \times Label \times (Row \times Row) \times State \rightarrow State \\
	\Psi(CopyProperty(l_s, l_t, l_p, f_m), s) = \inference{\exists c \in classes(s) : name(c) = l_s \\ \wedge \exists p \in properties(c) : name(p) = l_p }{application(s) \circ addProp(l_t, p)} 
	\\\\
	\Phi(CopyProperty(l_s, l_t, l_p, f_m), s) = \begin{cases}
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) \leq 1 }{\begin{gathered}
			database(s) \bullet copyColumn(l_s, l_t, l_p) \\ \bullet copyValues(l_s, l_t, l_p, f_m) 
			\end{gathered}} \\ \\
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) > 1}{\begin{gathered}
			database(s) \bullet copyTable(l_s + l_p, l_t + l_p) \\ \bullet copyRows(l_s + l_p, l_t + l_p, f_m) 
			\end{gathered}}
 \end{cases}
\end{align*}

>>>>

\paragraph{Add Table} The transformation creates a new table in the database. The new table should not contain any foreign keys.
\begin{align*}
	\mathbf{addTable} : Table* \times Database \rightarrow Database \\ 
	addTable(t, d) = \begin{cases}
		\inference{|t| > 1}{d \bullet addTable(head(t)) \bullet addTable(tail(t))}
\\ \\	
		\inference{|t| = 1 \wedge \forall e \in tables(d) \wedge name(t) \neq name(e) \\ \wedge \forall f \in foreignKeys(t) : \\ s\exists e \in tables(d) \wedge name(e) = reference(f) }{tables(d) \cup t}
\\ \\
		Inconsistent \;d 
	 \end{cases}\\ 
	t = Table*, d \lhd Database
\end{align*}

@@

The $CopyProperty$ function can be implemented as a transformation composed by operations for adding and removing property, nevertheless this composition would not work with instances, therefore transformation to update data are used.
\begin{align*}
	\mathbf{CopyProperty} : Label \times Label \times Label \times (Row \times Row) \times State \rightarrow State \\
	\Psi(CopyProperty(l_s, l_t, l_p, f_m), s) = \inference{\exists c \in classes(s) : name(c) = l_s \\ \wedge \exists p \in properties(c) : name(p) = l_p }{application(s) \circ addProp(l_t, p)} 
	\\\\
	\Phi(CopyProperty(l_s, l_t, l_p, f_m), s) = \begin{cases}
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) \leq 1 }{\begin{gathered}
			database(s) \bullet copyColumn(l_s, l_t, l_p) \\ \bullet copyValues(l_s, l_t, l_p, l_p, f_m) 
			\end{gathered}} \\ \\
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) > 1}{\begin{gathered}
			database(s) \bullet copyTable(l_s + l_p, l_t + l_p) \\ \bullet copyRows(l_s + l_p, l_t + l_p, f_m) 
			\end{gathered}}
 \end{cases}
\end{align*}
